%-----------------------------------------
% URL: http://github.com/mdwrigh2/resume
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[darkred]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information 
\firstname{Chris}
\familyname{Fox}
\mobile{(360) 609-5854}
\email{chrisdavidfox@gmail.com}
\homepage{cdfox.github.io}

\title{}

\nopagenumbers{}

\begin{document}

\maketitle

\section{Education}
  \cventry{2016 {\footnotesize (expected)}}{PhD Computer Science}{North Carolina State University}{Raleigh, NC}{}{%GPA: 3.5
  Research Focus: Modeling User Knowledge in a Tutorial Dialogue System
  }
  \cventry{2012}{MS Computer Science}{North Carolina State University}{Raleigh, NC}{}{%GPA: 3.5
  }
  \cventry{2009}{BS Mathematics,  BS Economics}{University of Washington}{Seattle, WA}{}{%GPA: 3.4
  }

\section{Skills}
  \cvline{}{Python, Java, C++, Javascript/HTML/CSS, Android, iOS, Matlab, R }

\section{Experience} 
  \cventry{May 2014 -- Aug 2014}{Software Engineering Intern}{Google}{New York, NY}{}{
    \begin{itemize}
      \item Prototyped an improvement to a tool for Adwords customers.
      \item  Forecasting, distributed data-processing pipelines, web-based visualization, C++
    \end{itemize}
  }
  \cventry{Aug 2013 -- May 2014}{Teaching Assistant}{North Carolina State University}{Raleigh, NC}{}{
    \begin{itemize}
      \item Spoken Dialogue Systems
      \item Graph Theory
    \end{itemize}
  }
  \cventry{May 2013 -- Aug 2013}{Software Engineering Intern}{Apple}{Cupertino, CA}{}{
    \begin{itemize}
      \item Researched, implemented, and tested a new load balancing scheme for the Game Center backend.
      \item Built a web-based visualization to show estimated improvement under the new system.
      \item Hadoop, HBase
    \end{itemize}
  }
  \cventry{Jan 2012 -- May 2013}{Research Assistant}{North Carolina State University}{Raleigh, NC}{}{
    \begin{itemize}
      \item Modified Latent Dirichlet Allocation, a probabilistic model of latent thematic structure in a text corpus, to learn topics that change with time but have stable core.
      \item Used Gibbs sampling to fit a model to the corpus of 32K news articles gathered using the Twitter API.
      \item Separately, mentored an undergraduate on a project to build a speech-based physics tutor on Android.
    \end{itemize}
  }
\cventry{Sept 2009 -- June 2010}{Research Assistant}{University of Washington}{Seattle, WA}{}{
    \begin{itemize}
      \item Built an HTML Canvas-based player to display dynamically generated animations of flow cytometry data.
      \item Used Python to produce a KML visualization in Goolge Earth from flow cytometry data.    \end{itemize}
  }
\section{Selected Graduate Coursework}
  \cvline{}{   \vspace{-5mm}
   \begin{itemize}
   \item Machine Learning
   \item Spoken Dialogue Systems
   \item Probabilistic Graphical Models
   \item Automated Learning and Data Analysis
   \end{itemize}
   \vspace{-5mm}
  }
\section{Projects}
  \cvline{}{   \vspace{-5mm}
   \begin{itemize}
   \item \textbf{Route Tracing Study.} Used cross-validated lasso regression to find dialogue features predictive of better learning in a set of route teaching dialogues.
   \item \textbf{SouffleTutor.} Built voice-controlled guide on iOS for making a souffle. 
   \end{itemize}
   \vspace{-5mm}
  }
\end{document}
